A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
small changes

There has also been much recent work on scaling offline approximate
POMDP solution procedures to medium-sized instances. Recent
contributions propose more efficient belief-point sampling
schemes~\cite{kurniawati:etal:2010,shani:etal:08}, and factored
representations with procedures that can efficiently exploit
structures in those
representations~\cite{brunskill:russell:2010,shani:etal:2008}. Offline
domain independent systems scale to {\em logistics} problems with
$2^{22}$ states~\cite{shani:etal:2008}, taking over an hour to
converge, and around 10 seconds on average to perform each Bellman
backup. \citeauthor{brunskill:russell:2010} are able to solve problems
with approximately $10^{30}$ states, by further exploiting certain
problem features -- E.g., problems where no actions with negative
effects.
%%
Moving someway towards supporting real-time decision making, recent
online POMDP solution procedures have been developed which leverage
highly approximate value functions -- computed using an offline
procedure -- and heuristics in forward
search~\cite{ross:etal:2008}. These approaches are applicable in
relatively small problems, and can require
expensive \emph{problem-specific} offline processing in order to yield
good behaviours.
%%
A {\em very} recent and promising online approach for
larger POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.

>>>>

There has also been much recent work on scaling offline approximate
POMDP solution procedures to medium-sized instances. Recent
contributions propose more efficient belief-point sampling
schemes~\cite{kurniawati:etal:2010,shani:etal:08}, and factored
representations with procedures that can efficiently exploit
structures in those
representations~\cite{brunskill:russell:2010,shani:etal:2008}. Offline
domain independent systems scale to {\em logistics} problems with
$2^{22}$ states~\cite{shani:etal:2008}, taking over an hour to
converge, and around 10 seconds on average to perform each Bellman
backup. \citeauthor{brunskill:russell:2010} are able to solve problems
with approximately $10^{30}$ states, by further exploiting certain
problem features -- E.g., problems where no actions have negative
effects.
%%
Moving someway towards supporting real-time decision making, recent
online POMDP solution procedures have been developed which leverage
highly approximate value functions -- computed using an offline
procedure -- and heuristics in forward
search~\cite{ross:etal:2008}. These approaches are applicable in
relatively small problems, and can require
expensive \emph{problem-specific} offline processing in order to yield
good behaviours.
%%
A {\em very} recent and promising online approach for
larger POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}. 
%%
Our approach can also be thought of as an online POMDP solver that
uses a sequential plan to guide the search, rather than (e.g.,
Monte-Carlo) sampling. Also, compared to most online POMDP procedures, which
replan at each step, our approach involves relatively little replanning.

%% Our approach requires minimal DT replanning,
%% preferring

%% Also, our approach will execute a few
%% actions (as much as it can before an assumption is found to be true or
%% false) before needing to plan again, rather than planning after each
%% step.

%% Moving someway towards supporting real-time decision making, recent
%% online POMDP solution procedures have been developed which leverage
%% highly approximate value functions -- computed using an offline
%% procedure -- and heuristics in forward
%% search~\cite{ross:etal:2008}. These approaches are applicable in
%% larger problems (\cite{ross:etal:2008} includes experiments in a domain
%% with around 12 thousand states), but the fact they often require
%% expensive \emph{problem-specific} offline processing in order to yield
%% good behaviours means they are impractical in problems as large as ours.
%% %%
%% A recent and promising online approach for
%% larger POMDPs employs Monte-Carlo sampling to break the curse of
%% dimensionality in situations where goal reachability is {\em easily}
%% determined~\cite{silver:veness:2010}. Our approach can also be thought of
%% as an online POMDP solver, but uses the sequential plan to guide the
%% search
%% for a decision-theoretic plan, rather than Monte-Carlo sampling. In
%% addition, our approach will execute a few actions (as much as it can
%% before
%% an assumption is found to be true or false) before needing to plan again,
%% rather than planning after each step.

%% [have a look at the bit in parentheses above, I'm not sure I quite
%% characterised how much plan it executes before replanning satisfactorally]
